\documentclass[11pt,letter]{article} 
\usepackage[top=1.00in, bottom=1.0in, left=1.1in, right=1.1in]{geometry}
\renewcommand{\baselinestretch}{1.5}

\def\labelitemi{--}
\begin{document}

\title{Soil Sample Plating Protocol} 
\date{\today}
\maketitle

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\subsection{Prepare soil solutions}
\begin{enumerate}
\item Use a sterilized spoon to collect soil from four corners and the center of the plot.

\item Mix the soil in a sterilized tube and label the tube.

\item After bringing the soil back to the lab, mix the soil well using a vortex.

\item Weigh 1 g of soil and add it to another sterilized tube.

\item Add 9 ml of distilled water; this will be the 10$^{-1}$ soil solution.

\item Mix the soil solution well using the vortex, then let it sit for a few minutes until the top layer of the liquid is relatively clear.

\item Use a pipette to take 1 ml of liquid from the 10$^{-1}$ soil solution and add it to another sterilized tube. Add 9 ml of distilled water; this will be the 10$^{-2}$ soil solution.

\item Use the same method to dilute the soil solution until obtaining the 10$^{-6}$ soil solution.

\item Keep the soil solutions in cold storage if not used immediately; the soil solutions should be used within 48 hours.
\end{enumerate}

\subsection{Plating}
\begin{enumerate}
\item Prepare agar medium with antibiotics and autoclave it to sterilize.

\item Pour plates while the agar is still warm but not too hot.

\item Allow the plates to cool completely; do not move the plates after pouring.

\item Use a pipette to dispense 1 ml of soil solution onto the surface of the agar. Add 3--5 sterilized glass beads and gently roll them across the agar surface to ensure even distribution of the liquid. Pour off the beads and any remaining liquid.

\item Put the lid on immediately and label the plate.

\item Seal the plates with Parafilm.

\item Incubate the plates upside down at room temperature for at least 3 days. (If the plates are accidentally not kept upside down and condensation forms on the lid, a warm water bag can be made by adding warm water to a Ziploc bag. Place the plate upside down on top of the warm water bag for a few minutes, then perform observations quickly.)
\end{enumerate}

\end{document}
